---
format: html
execute:
  echo: false
  warning: false
---
## ALS Data thinning

Inspect data to get an idea about differences in data and effects of pulse-based thinning


```{r}
source("scripts/functions.R")
source("config.R")
```

### Basic file info
:::: {.panel-tabset}

#### Leaf-on
::: {.panel-tabset}
##### raw
```{r}
vpc_leafon_raw |> print_fileinfo()
```

##### harmonized
```{r}
vpc_leafon_harmonized |> print_fileinfo()
```

##### ppm20
```{r}
vpc_leafon_ppm20 |> print_fileinfo()
```

##### ppm10
```{r}
vpc_leafon_ppm10 |> print_fileinfo()
```

##### ppm4
```{r}
vpc_leafon_ppm4 |> print_fileinfo()
```
:::

#### Leaf-off
::: {.panel-tabset}

##### raw
```{r}
vpc_leafoff_raw |> print_fileinfo()
```

##### harmonized
```{r}
vpc_leafoff_harmonized |> print_fileinfo()
```

##### ppm20
```{r}
vpc_leafoff_ppm20 |> print_fileinfo()
```

##### ppm10
```{r}
vpc_leafoff_ppm10 |> print_fileinfo()
```

##### ppm4
```{r}
vpc_leafoff_ppm4 |> print_fileinfo()
```
:::

::::


### Coverage
::: {.panel-tabset}

#### Leaf-on
```{r}
plot_extent(vpc_leafon_raw)
```

#### Leaf-off
```{r}
plot_extent(vpc_leafoff_raw)
```
:::



### Point/Pulse density I
:::: {.panel-tabset}

#### Leaf-on
::: {.panel-tabset}
##### raw
```{r}
vpc_leafon_raw |> managelidar::get_density() |> select(c(pointdensity, pulsedensity))
```

##### harmonized
```{r}
vpc_leafon_harmonized |> managelidar::get_density() |> select(c(pointdensity, pulsedensity))
```

##### ppm20
```{r}
vpc_leafon_ppm20 |> managelidar::get_density() |> select(c(pointdensity, pulsedensity))
```

##### ppm10
```{r}
vpc_leafon_ppm10 |> managelidar::get_density() |> select(c(pointdensity, pulsedensity))
```

##### ppm4
```{r}
vpc_leafon_ppm4 |> managelidar::get_density() |> select(c(pointdensity, pulsedensity))
```
:::

#### Leaf-off
::: {.panel-tabset}

##### raw
```{r}
vpc_leafoff_raw |> managelidar::get_density() |> select(c(pointdensity, pulsedensity))
```

##### harmonized
```{r}
vpc_leafoff_harmonized |> managelidar::get_density() |> select(c(pointdensity, pulsedensity))
```

##### ppm20
```{r}
vpc_leafoff_ppm20 |> managelidar::get_density() |> select(c(pointdensity, pulsedensity))
```

##### ppm10
```{r}
vpc_leafoff_ppm10 |> managelidar::get_density() |> select(c(pointdensity, pulsedensity))
```

##### ppm4
```{r}
vpc_leafoff_ppm4 |> managelidar::get_density() |> select(c(pointdensity, pulsedensity))
```
:::

::::



### Point/Pulse density II

#### Leaf-on vs. Leaf-off
::: {.panel-tabset}
##### raw
```{r}
plot_density_comparison(vpc_leafoff_raw, vpc_leafon_raw)
```

##### ppm20
```{r}
plot_density_comparison(vpc_leafoff_ppm20, vpc_leafon_ppm20)
```

##### ppm10
```{r}
plot_density_comparison(vpc_leafoff_ppm10, vpc_leafon_ppm10)
```

##### ppm4
```{r}
plot_density_comparison(vpc_leafoff_ppm4, vpc_leafon_ppm4)
```
:::



### Pulse penetration rate I
:::: {.panel-tabset}

#### Leaf-on
::: {.panel-tabset}
##### raw
```{r}
vpc_leafon_raw |> print_pulseinfo()
```

##### harmonized
```{r}
vpc_leafon_harmonized |> print_pulseinfo()
```

##### ppm20
```{r}
vpc_leafon_ppm20 |> print_pulseinfo()
```

##### ppm10
```{r}
vpc_leafon_ppm10 |> print_pulseinfo()
```

##### ppm4
```{r}
vpc_leafon_ppm4 |> print_pulseinfo()
```
:::

#### Leaf-off
::: {.panel-tabset}

##### raw
```{r}
vpc_leafoff_raw |> print_pulseinfo()
```

##### harmonized
```{r}
vpc_leafoff_harmonized |> print_pulseinfo()
```

##### ppm20
```{r}
vpc_leafoff_ppm20 |> print_pulseinfo()
```

##### ppm10
```{r}
vpc_leafoff_ppm10 |> print_pulseinfo()
```

##### ppm4
```{r}
vpc_leafoff_ppm4 |> print_pulseinfo()
```
:::

::::


### Pulse penetration rate II

#### Leaf-on vs. Leaf-off
::: {.panel-tabset}
##### raw
```{r}
plot_penetration_comparison(vpc_leafoff_raw, vpc_leafon_raw)
```

##### ppm20
```{r}
plot_penetration_comparison(vpc_leafoff_ppm20, vpc_leafon_ppm20)
```

##### ppm10
```{r}
plot_penetration_comparison(vpc_leafoff_ppm10, vpc_leafon_ppm10)
```

##### ppm4
```{r}
plot_penetration_comparison(vpc_leafoff_ppm4, vpc_leafon_ppm4)
```
:::
